### 2021-03-13 chapters/2-background_and_related_work.tex
überarbeitungen
Anfang und ende fertig
Einleitung überarbeitet

This chapter covers three important topics, following chapters rely on.

Identity Management Provisioning is introduced as a new identity management method. Its features along with system components and important use cases are described.

The Online Access Law is introduced as a currently relevant regulation with special requirements for identity management. The most important regulations as well as resulting system architectures for its implementation are described.

Messaging is introduced as a way of designing integration architectures. Multiple messaging patterns as well as their visual notation are described.

\section{Identity Management Provisioning (IMP)}
\subfile{sections/5-imp}

\section{Online Access Law (OZG)}
\subfile{sections/6-online_access_law}

\section{Messaging}
\subfile{sections/7-messaging}

>>>>

This chapter covers three important topics that the following chapters rely on. Identity Management Provisioning as approach to solve problems of distributed partial identities is described along with possible services and systems. The most important regulations of the Online Access Law as well as its basic use case and resulting system architecture of a federal state are described. Messaging is presented as a way of designing technological integration architectures. Multiple messaging patterns as well as their visual notation are explained.

\section{Identity Management Provisioning (IMP)} \label{imp}
\subfile{sections/5-imp}

\section{Online Access Law (OZG)} \label{ozg}
\subfile{sections/6-online_access_law}

\section{Messaging} \label{messaging}
\subfile{sections/7-messaging}

### 2021-03-13 chapters/sections/1-context.tex
Einleitung überarbeitet

Many services, are accessible through the internet. Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns. Online Service Providers (SP) often require customers to create user profiles in order to access their services. Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail. It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.

In some cases, user profiles are required by Service Providers even if their service could be provided without them. Especially in case of small stores, running their individual online shop, user profiles are not necessary for customers to place an order. Personal information can be shared temporarily until processing of the order is completed and the package delivered. Some online shops allow users to place orders by temporarily sharing personal information, which however, limits interaction and communication possibilities to insecure e-mail exchange.

A method for identity management called Identity Management Provisioning (IMP) is introduced. IMP provides identity management as a service to users and Service Providers. It enables users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages". Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be used in different ways. It can be used to create and manage a persistent user profile or to temporarily share personal information for a business process. IMP messages enable user and Service Provider to securely exchange structured data and depending on the client application which receives and displays the data, design rich user interactions.

>>>>

Today, many services are accessible through the internet. Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns. Online Service Providers (SP) often require customers to create user profiles in order to access their services. Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail. It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.

In some cases, user profiles are required by Service Providers even if they are not necessary. Especially in case of small stores, running their individual online shops, user profiles are not necessary for customers to place an order. Personal information can be shared temporarily until processing of the order is completed and the package delivered. Some online shops allow users to place orders by temporarily sharing personal information, which however, limits interaction and communication possibilities to insecure e-mail exchange.

A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG). It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services. Federal republic and each member state operate their individual user profile systems accessible through their administration portals.

The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals. To solve this problem, a solution for making OZG user profiles "interoperable" is in development. However, interoperable user profiles can not be accessed by the private sector.

Identity Management Provisioning (IMP) is an approach to identity management which aims to solve problems of distributed partial identities by enabling users to bring their online identities with them, when accessing systems of Service providers. It provides identity management as a service to users and Service Providers by enabling users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages". Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be utilized in different ways. It can for example be used to create and manage a persistent SP user profile or to temporarily share personal information for a business process of a SP. IMP messages enable user and Service Provider to securely exchange structured data and depending on the client application which receives and displays the data, design rich user interactions. This approach to identity management could be an alternative to user profiles in the private sector and in context of the OZG.

Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to for example access personal information and perform authentication. They also play an important role in the design of business processes. Therefore, for Service Providers to utilize IMP, integration into existing business processes and existing system architectures is necessary.

### 2021-03-13 chapters/sections/11-technological_integration.tex
Einleitung überarbeitet

In this section an integration architecture is presented for integration of the IMP system presented in section 2.2 into the existing OZG system architecture presented in section 3.3.

@@

\subsection{Messaging}
A messaging approach is used for the technological integration. As described in section 2.4, messaging enables the systems to access each others services in a decoupled way. This is a useful feature as the integration architecture should be reusable for different system architectures. The messaging patterns described in 2.4 also enable the integration architecture to be configured according to changes in the operation of the existing systems. The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
    \caption{Insertion of Integration Systems into OZG System Architecture}
    \label{integration1:integration_overview}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
    \caption{Onboarding Overview}
    \label{integration1:onboarding_overview}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
    \caption{Messaging Integration}
    \label{integration1:messaging_integration}
\end{figure}

@@

On the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system. The adapters communicate with the messaging system through channels. Messages placed on each channel can be simultaneously accessed by multiple systems. Using these channels, message adapters can send requests and replies, and receive replies, notifications and requests

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
    \caption{Messaging System Overview}
    \label{integration1:messaging_system_overview}
\end{figure}

The figure gives an overview of the messaging system which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.

As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which it is built upon. As described in section 2.2, communication between IMP identity and Service Provider is only possible through an established relationship.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/6. Onboarding Template Module.pdf}
    \caption{Onboarding Template Module}
    \label{integration1:onboarding_template_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/7. Onboarding Request Module.pdf}
    \caption{Onboarding Request Module}
    \label{integration1:onboarding_request_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
    \caption{Onboarding Relationship Module}
    \label{integration1:onboarding_relationship_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Relationship Mapping.pdf}
    \caption{Relationship Mapping Module}
    \label{integration1:relationship_mapping_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Message Mapping Module.pdf}
    \caption{Message Mapping Module}
    \label{integration1:message_mapping_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. Attribute Change Message Module.pdf}
    \caption{Attribute Change Message Module}
    \label{integration1:attribute_change_message_module}
\end{figure}

For the messaging system to process messages being exchanged as part of relationships, message modules can be added. Their purpose is to map messages of certain types onto the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them. They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.

In this case an "Attribute Change Message Module" is included, which processes messages related to the attribute change process. Messages exchanged through IMP relationships can have arbitrary content. However, the messages are assumed to contain a message type attribute and a message content attribute. Based on the message type attribute a message filter can let messages through that contain a message type attribute correlating to an attribute change process. Based on the type of a message, a content based message router then copies each message to a datatype channel. In this example, messages of type attribute change request and attribute change established are distinguished. Corresponding to that, two data type channels exist. As based on the channel, a message is placed, its message type can be inferred, content filters remove the message type attributes.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Attribute Change Request Module.pdf}
    \caption{Attribute Change Request Module}
    \label{integration1:attribute_change_request_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. User Profile Attribute Sync Module.pdf}
    \caption{User Profile Attribute Sync Module}
    \label{integration1:user_profile_attribute_sync_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Mail Message Module.pdf}
    \caption{Mail Message Module}
    \label{integration1:mail_message_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Mail Module.pdf}
    \caption{Mail Module}
    \label{integration1:mail_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/16. Authenticatin Message Module.pdf}
    \caption{Authentication Message Module}
    \label{integration1:authentication_message_module}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/17. Authentication.pdf}
    \caption{Authentication Module}
    \label{integration1:authentication_module}
\end{figure}

>>>>

In this section an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
    \caption{Insertion of Integration Systems into OZG System Architecture}
    \label{integration1:integration_overview}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
    \caption{Onboarding Overview}
    \label{integration1:onboarding_overview}
\end{figure}

@@

A messaging approach is used for the technological integration. As described in section \ref{messaging}, messaging enables the systems to access each others services in a decoupled way. This is a useful feature as the integration architecture should be reusable for different system architectures. The messaging patterns described in section \ref{messaging} also enable the integration architecture to be configured according to changes in the operation of the existing systems. The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
    \caption{Messaging Integration}
    \label{integration1:messaging_integration}
\end{figure}

@@

As shown in figure \ref{integration1:messaging_integration}, on the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system. The adapters communicate with the messaging system through channels. Messages placed on each channel can be simultaneously accessed by multiple systems. Using these channels, message adapters can send requests and replies, and receive replies, notifications and requests

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
    \caption{Messaging System Overview}
    \label{integration1:messaging_system_overview}
\end{figure}

Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.

As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which it is built upon. As described in section \ref{imp}, communication between IMP identity and Service Provider is only possible through an established relationship.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/6. Onboarding Template Module.pdf}
    \caption{Onboarding Template Module}
    \label{integration1:onboarding_template_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/7. Onboarding Request Module.pdf}
    \caption{Onboarding Request Module}
    \label{integration1:onboarding_request_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
    \caption{Onboarding Relationship Module}
    \label{integration1:onboarding_relationship_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Relationship Mapping.pdf}
    \caption{Relationship Mapping Module}
    \label{integration1:relationship_mapping_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Message Mapping Module.pdf}
    \caption{Message Mapping Module}
    \label{integration1:message_mapping_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. Attribute Change Message Module.pdf}
    \caption{Attribute Change Message Module}
    \label{integration1:attribute_change_message_module}
\end{figure}

For the messaging system to process messages being exchanged as part of relationships, message modules can be added. Their purpose is to map messages of certain types from the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them. They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.

In this case an "Attribute Change Message Module" is included, which processes messages related to the attribute change process. Messages exchanged through IMP relationships can have arbitrary content. However, the messages are assumed to contain a message type attribute and a message content attribute. Based on the message type attribute a message filter can let messages through that contain a message type attribute correlating to an attribute change process. Based on the type of a message, a content based message router then copies each message to a datatype channel. In this example, messages of type attribute change request and attribute change established are distinguished. Corresponding to that, two data type channels exist. As the type of a message can be inferred from the channel it is placed on, content filters can remove the message type attributes.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Attribute Change Request Module.pdf}
    \caption{Attribute Change Request Module}
    \label{integration1:attribute_change_request_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. User Profile Attribute Sync Module.pdf}
    \caption{User Profile Attribute Sync Module}
    \label{integration1:user_profile_attribute_sync_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Mail Message Module.pdf}
    \caption{Mail Message Module}
    \label{integration1:mail_message_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Mail Module.pdf}
    \caption{Mail Module}
    \label{integration1:mail_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/16. Authenticatin Message Module.pdf}
    \caption{Authentication Message Module}
    \label{integration1:authentication_message_module}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/17. Authentication.pdf}
    \caption{Authentication Module}
    \label{integration1:authentication_module}
\end{figure}

### 2021-03-13 chapters/sections/14-technological_integration.tex
Einleitung überarbeitet

Focus of the technological integration is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions. The layout of the messaging system should not change and the purpose of each module should stay the same. In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
    \caption{Integration Overview}
    \label{integration2:integration_overview}
\end{figure}

To implement the IMP solution, a connector is included in the existing system architecture of each institution as well as the messaging system described in section 4.2. Instead of the web server and service facade in the portal domain, the messaging system is connected to the web server and institution system of the institution domain.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
    \caption{Service Application Overview}
    \label{integration2:application_overview}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
    \caption{Messaging Overview}
    \label{integration2:messaging_overview}
\end{figure}

@@

On the "Relationship to Identity Integration Layer", modules exist for establishing the different types of application relationships. For simplification, modules only for an "Application A" are shown. Besides the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module. As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately. For an established relationship, instead of issuing the existing system architecture to create a user profile, the application relationship module issues the existing system architecture to process an application based on the attributes shared as part of the relationship. And instead of a user profile ID, the existing system architecture responds with an application process ID. This application process ID is used in the same way as the user profile ID in section 4.2. Through the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.

>>>>

Focus of the technological integration is to use the messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions. The layout of the messaging system should not change and the purpose of each module should stay the same. In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
    \caption{Integration Overview}
    \label{integration2:integration_overview}
\end{figure}

As shown in figure \ref{integration2:integration_overview}, to implement the IMP solution, a connector as well as the messaging system described in section 4.2 is included in the existing system architecture of each institution. Instead of the web server and service facade in the portal domain, the messaging system is connected to the web server and institution system of the institution domain.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
    \caption{Service Application Overview}
    \label{integration2:application_overview}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
    \caption{Messaging Overview}
    \label{integration2:messaging_overview}
\end{figure}

@@

On the "Relationship to Identity Integration Layer", modules exist for establishing the different types of application relationships. For simplification, modules only for an exemplary application process "Application A" are shown. Although the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module. As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately. For an established relationship, instead of issuing the existing system architecture to create a user profile, the application relationship module issues the existing system architecture to process an application based on the attributes shared as part of the relationship. And instead of a user profile ID, the existing system architecture responds with an application process ID. This application process ID is used in the same way as the user profile ID in section 4.2. Through the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.

### 2021-03-13 chapters/sections/2-objective.tex
Einleitung überarbeitet

Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.

In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.

Two solutions for IMP integration and one message based IMPS integration architecture are presented.

The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management. In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them. This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.

In the second solution, IMP is used as an alternative way for identity management without user profiles. This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.

The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers. This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.

>>>>

The bachelor thesis uses the scenario of the OZG as a small scale model for the general problem of distributed partial identities. Focus is the utilization and system integration of IMP for Service Providers with existing user profile based system architectures. A federal state, in context of the OZG, is used as an example for a Service Provider.

One objective of the bachelor thesis is to examine problems of user profile based identity management and interoperable OZG user profiles and describe to what extend IMP as an approach can be a solution.

Another objective of the bachelor thesis is to design "IMP solutions" which describe possibilities of how IMP services and tools can be concretely utilized on the example of - but not limited to - the OZG use case. IMP solutions demonstrate how IMP relationships and IMP messages can be utilized by users and Service Providers to share personal information and interact in order to solve problems of distributed partial identities related to usability, data protection and security.

Using OZG as an example, another objective of the bachelor thesis is to design a technological integration architecture for integration of IMP solutions into existing system architectures of Service Providers. Its integration capabilities, however, can not be limited to one IMP solution and one system architecture. On the contrary, it has to be capable of integrating various IMP solutions into different system architectures. The integration system therefore has to be configurable and expandable according to requirements of new IMP solutions and system architectures. To demonstrate the capabilities of the integration architecture in theory, IMP solutions presented as part of the thesis, have to be integrated into different system architectures in the context of the OZG.

IMP solutions and integration architecture presented in the bachelor thesis must not be tightly fitted to the scenario of the OZG but have to also be utilizable by Service Providers in other contexts.

### 2021-03-13 chapters/sections/3-structure_of_work.tex
Einleitung überarbeitet

In the chapter "Background and Related Work" important topics, following chapters rely on are covered.
In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well ass possible solutions trough IMP.
In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Replacing IMP Utilization" the second IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Conclusion" the most important results of the thesis are summarized and possible future developments and contributions are discussed.

>>>>

The chapter "Background and Related Work" covers important topics that following chapters rely on. 
The chapter "User Profile Identity Management" describes disadvantages of user profile based identity management in general as well as in context of the OZG. Possible solutions through IMP are described. 
The chapter "IMP Utilization as Extension" presents the first IMP solution as well as its integration through the technological integration architecture.
The chapter "IMP Utilization as Replacement" presents the second IMP solution as well as its integration through the technological integration architecture.
The chapter "Conclusion" summarizes the most important results of the thesis and mentions possible future developments and contributions.

### 2021-03-13 chapters/sections/6-online_access_law.tex
Einleitung überarbeitet

This chapter gives an overview about the Online Access Law regarding its regulations, their implementation and the underlying system architecture.

@@

\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.  As it is not clear which administrative services exactly are included by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.

@@

Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions. The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:

A digitized administrative service can be accessed by a user through a website. The website is hosted either by the federal republic or a federal state and is called "Administration Portal". Access is usually provided through an application form. The administrative service can be managed through a user profile which is provided by the federal republic or the member state. Management of an administrative service usually includes starting the service by sending in a form, communicating with the responsible institutions through the inbox of the profile and receiving a result. The user profile can also enable users to upload documents to a datawallet and to save personal information for automatically filling in forms.

@@

As shown in figure \ref{ozg:system_overview}, the OZG system architecture is separated into three components and two domains. Domains in this context describe the operation of systems they contain in separate physical locations. Components in this context describe functionally correlated systems of a system architecture.

>>>>

This chapter gives an overview about the Online Access Law regarding its regulations, their implementation, the basic OZG use case and the underlying system architecture.

@@

\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.  As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.

@@

The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way: A digitized administrative service can be accessed by a user through a website. The website is hosted either by the federal republic or a federal state and is called "Administration Portal". Access is usually provided through an application form. The administrative service can be managed through a user profile which is provided by the federal republic or the member state. Management of an administrative service usually includes starting the service by sending in a form, communicating with the responsible institutions through the inbox of the profile and receiving a result. The user profile can also enable users to upload documents to a datawallet and to save personal information for automatically filling in forms.

@@

As shown in figure \ref{ozg:system_overview}, the OZG system architecture is separated into three components and two domains. Domains in this case separate systems in regard to the physical location where they operate. Components in this case describe functionally correlated systems of a system architecture.
